Solving Collective Spin Hamiltonians with Decoherence

### 2018-10-02 soc_squeezing/cumulant_expansions.tex
improved some notations

  = \sum_{s\ge0} \sum_{\p{\v J,\v K,\v r;\v m,\v n,s}}
  f_{\v m\v n\v r} P_{\v J} Q_{\v K},

@@

over $\p{\v J,\v K,\v r;\v m,\v n,s}$ denotes a sum over all values of
$\v J,\v K,\v r$ with the restrictions

@@

  \sum_{\mu,\nu} r_{\mu\nu} = s,

@@

@@

  \bigotimes_{\kappa\ne0}

@@

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v\ell,\v r,\v\rho;\v m,\v n,s}}
  f_{\v m\v n\v r} g_{\v\rho} \v\eta_{\v\rho} c_{\v\ell\v\rho} P_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where in addition to \eqref{eq:rest_r} the sum over
$\p{\v\ell,\v r,\v\rho;\v m,\v n,s}$ enforces the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \abs{\v\ell} \equiv \abs{\set{\ell^\mu_a}}
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv { N - \abs{\v\ell} \choose \sum_{\mu,\nu}\rho^{\mu\nu}_0},
\end{align}
accounts for the multiplicity of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.

For clarity, we note here that all indices on
$m_\mu,n_\mu,r_{\mu\nu},\eta_{\mu\nu\kappa},\rho^{\mu\nu}_\kappa$ and
the upper index on $\ell^\mu_a$ take on the same values as the indices
on elements $\sigma_\mu$ of some complete basis for single-spin
operators; of these, only the last index ($\kappa$) on
$\eta_{\mu\nu\kappa},\rho^{\mu\nu}_\kappa$ ever matches the index for
the identity element $\sigma_0\equiv\1$.  The lower index on
$\ell^\mu_a$ indexes the $a$-th spin acted on by a $\sigma_\mu$
operator in each term of \eqref{eq:SS_simp}.

>>>>

  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}}
  \sum_{\p{\v J,\v K;\v m,\v n,\v r}} f_{\v m\v n\v r} P_{\v J} Q_{\v K},

@@

over $\p{\v r;\v m,\v n,s}$ denotes a sum over all values of $\v r$ with the restrictions

@@

  \sum_{\mu,\nu} r_{\mu\nu} = s;

@@

the sum over $\p{\v J,\v K;\v m,\v n,\v r}$ denotes a sum over all
values of $\v J,\v K$ with the restrictions

@@

  \otimes \bigotimes_{\kappa\ne0}

@@

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} \sum_{\p{\v\rho;\v r}}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  f_{\v m\v n\v r} g_{\v\rho} \v\eta_{\v\rho} c_{\v\ell\v\rho} P_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \abs{\set{\ell^\mu_a}}
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv { N - \abs{\v\ell} \choose \sum_{\mu,\nu}\rho^{\mu\nu}_0},
\end{align}
with $\abs{\v\ell}$ equal to the number of elements in $\v\ell$,
accounts for the multiplicity of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.

For clarity, we note here that all indices on
$m_\mu,n_\mu,r_{\mu\nu},\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ and
the upper index on $\ell^\mu_a$ take on the same values as the indices
on elements $\sigma_\mu$ of some complete basis for single-spin
operators; of these, only the last index ($\kappa$) on
$\rho^{\mu\nu}_\kappa,\eta_{\mu\nu\kappa}$ ever matches the index for
the identity element $\sigma_0\equiv\1$.  The lower index on
$\ell^\mu_a$ indexes the $a$-th spin acted on by a $\sigma_\mu$
operator in each term of \eqref{eq:SS_simp}.
